Peer influences in air travel behavior: A social autoregressive analysis

### 2015-04-24 article/article.Rmd
Added descriptive table to document.

```{r load_user, warning=FALSE}
source("../rscripts/datacleaner.R")
```

@@

user <- user %>%
  left_join(number_trips)
```

@@

>>>>

```{r load_user, warning=FALSE, cache = FALSE}
source("../rscripts/datacleaner.R")
```

@@

user <- user %>%
  filter(!is.na(collected)) %>%
  left_join(number_trips) %>%
  mutate(number_trips = ifelse(is.na(number_trips), 0, number_trips))
```

@@

```{r survey_summary, echo = FALSE}
us <- user %>%
  summarise(n = n(),
            min_age = min(age, na.rm = TRUE),
            max_age = max(age, na.rm = TRUE),
            med_age = median(age, na.rm = TRUE),
            n_other = sum(race == "Other"),
            n_zero = sum(number_trips == 0),
            n_one = sum(number_trips == 1),
            n_two = sum(number_trips == 2),
            n_three = sum(number_trips == 3),
            n_fourplus = sum(number_trips >= 4)
            )
```

```{r summary_table, echo = FALSE}
t <- data_frame(
  "Variable" = c("Users:", "Responses", "Used records", 
                 "Minimum respondent age", "Median age", "Minorities",
                 "Trips:", "Zero trips", "One trip", "Two trips", 
                 "Three trips", "Four or more trips",
                 "Friends:",
                 "Total friends collected", "Unique friends",
                 "Unique hometowns", "Unique current locations"),
  " " = c("", n_collected, us$n, 
          us$min_age, us$med_age,  us$n_other, 
          "", us$n_zero, us$n_one, us$n_two, us$n_three, us$n_fourplus,
          "",
          nrow(friends), length(unique(friends$fbid)),
          length(unique(friends$from)), length(unique(friends$at)))
)
kable(t)
